---
title: "Computational Reproducibility"
author: "Fred LaPolla"
date: "10/14/2020"
output: html_document
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown file

This file, an R Markdown lets you combine plain text, in the white spaces, and code chunks, in the gray. The text is not really code, but can be used to communicate, while the code chunks let you combine the actual analysis you are running alongside the results. This means someone can see exactly what you did to get your results.

To add a chunk either click on the green Insert button and choose R or hit Command + Option + i (Mac) or Ctrl + Alt + i (PC)

```{r}
3+3
```

## Homework

1) Create an R Project to pull this file from GitHub. 

2) Please describe one of the ways that Wilson et. al. suggest is a good practice for computational reproducibility and how a tool like R can be used. Write your answer below.

Wilson describes the importance of clearly listing the names and versions
of packages used. This ensures that someone running the program far down
in the future is able to exactly reproduce the environment originally used. 
In addition, a tool like R allows researchers to write scripts in which
each line can serve as a "record" of how the data was manipulated and analyzed. 

3) Add a code chunk and find the square root of 4 to the 13th power. If you are unsure of what command to use, google it. 

```{r}
#There's no need to use the sqrt function, it's the same thing as taking
#the value to the 1/2 power
(4^0.5)^13
```
4) Push this homework to the GitHub repository for the homework. 





